### 2017-07-17 README.Rmd
update
Add difference in medians example to README

One categorical (2 level) variable (implemented up to calculate())

```
mtcars %>%
  specify(response = am) %>% # alt: am ~ 1
  hypothesize(null = "point", p = c("1" = .25)) %>% 
  generate(reps = 100, type = "simulate") %>% 
  calculate(stat = "prop")
```

Two categorical (2 level) variables (implemented)

@@

One categorical (>2 level) - GoF  (implemented)

@@

Two categorical (>2 level) variables  (implemented)

@@

One numerical variable one categorical (2 levels) (diff in means) (implemented)

@@

One numerical one categorical (>2 levels) -  ANOVA  (not yet implemented)

@@

>>>>

One categorical (2 level) variable

```
mtcars %>%
  specify(response = am) %>% # alt: am ~ NULL (or am ~ 1)
  hypothesize(null = "point", p = c("1" = .25)) %>% 
  generate(reps = 100, type = "simulate") %>% 
  calculate(stat = "prop")
```

Two categorical (2 level) variables

@@

One categorical (>2 level) - GoF

@@

Two categorical (>2 level) variables

@@

@@

One numerical variable one categorical (2 levels) (diff in medians)

```
mtcars %>%
  specify(mpg ~ am) %>% # alt: response = mpg, explanatory = am
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in medians")
```

One numerical one categorical (>2 levels) -  ANOVA

@@

Two numerical vars - SLR
